---
title: "2_4_merging_temperature_data"
author: "Aidan Coyle"
date: "7/25/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction

In the previous script, we fixed file structure issues in our temperature data. Now, we'll incorporate the temperature data, which is included in .txt files. This is going to be a pain, so buckle up. Main issues are as follows:

- Temperature data is directly from data loggers that were in the pots. This means that they include both time at the bottom and time on deck.

- In some years, data loggers are identified by the filename (T7 = Tidbit 7; Tidbit = data logger) in the temp data. In others, they're identified by survey number.

- Tidbit number may shift from year to year

- File structures differ substantially by year.

- Best file to examine differs from year to year! Sometimes Tidbit files are individually numbered, other times they're already amalgamated into a master sheet

Gameplan will be as follows:
- Go through each year individually due to differences in file structure
- Create master sheet of all 

Summary of file structures is as follows. Note: this is approximate, as some years have different structures for the two surveys (one may be Tanner -> LegNum.txt, the other may be RKC -> Leg -> num.txt)

Year -> Crab -> Leg -> num.txt
2011
2012
2013
2014
2015
2016
2017
2018
2019

Year -> CrabLeg -> num.txt
2006
2007
2008
2009
2010
2017


Year -> num,date.txt
2005

#### Load libraries (and install if necessary)

```{r libraries, message=FALSE, warning=FALSE}
# Add all required libraries here
list.of.packages <- c("tidyverse", "readxl", "lubridate", "rnaturalearth", "rnaturalearthdata", "sf", "rgeos")
# Get names of all required packages that aren't installed
new.packages <- list.of.packages[!(list.of.packages %in% installed.packages()[, "Package"])]
# Install all new packages
if(length(new.packages)) install.packages(new.packages)


# Load all required libraries
lapply(list.of.packages, FUN = function(X) {
  do.call("require", list(X))
})
```






